\begin{thebibliography}{99}

\bibitem{cfengine}
Mark Burgess, ``CFEngine: a system configuration engine'',
University of Oslo report 1993,
http://cfengine.com/markburgess/papers/cfengine\_history.pdf

\bibitem{cmt}
``Comparison of open-source configuration management software'',
http://en.wikipedia.org/wiki/Comparison\_of\_open\_source\_configuration\_management\_software.

\bibitem{puppet}
Luke Kanies,
``Puppet: Next-Generation Configuration Management'',
USENIX ;login, February 2006, Volume 31, Number 1
https://c59951.ssl.cf2.rackcdn.com/807-kanies\_0.pdf.

\bibitem{ec2}
``Release: Amazon EC2 on 2006-08-23'',
http://aws.amazon.com/releasenotes/Amazon-EC2/353.

\bibitem{agile manifesto}
``アジャイルソフトウェア開発宣言'',
http://agilemanifesto.org/iso/ja/.

\bibitem{agile infrastructure}
Patrick Debois,
``Agile infrastructure and operations: how infra-gile are you?'',
Agile, 2008. AGILE '08. Conference,
http://www.jedi.be/presentations/IEEE-Agile-Infrastructure.pdf.

\bibitem{test driven development}
Kent Beck,
``Test Driven Development: By Example'',
ISBN: 978-0321146533.

\bibitem{test driven infrastructure with chef}
Stephen Nelson-Smith,
``Test-Driven Infrastructure with Chef, 2nd Edition
Bring Behavior-Driven Development to Infrastructure as Code'',
ISBN: 978-1449372200.

\bibitem{chefspec}
``ChefSpec'', http://code.sethvargo.com/chefspec/.

\bibitem{rspec-puppet}
``rspec-puppet'', http://rspec-puppet.com/.

\bibitem{cucumber-chef}
``Cucumber-Chef'', http://www.cucumber-chef.org/.

\bibitem{minitest-chef-handler}
``minitest-chef-handler'', https://github.com/calavera/minitest-chef-handler.

\bibitem{test kitchen}
``Test Kitchen'', http://kitchen.ci/.

\bibitem{rspec-system}
``rspec-system'', https://github.com/puppetlabs/rspec-system.

\bibitem{rspec}
``RSpec``, http://rspec.info/.

\bibitem{minitest}
``minitest'', http://docs.seattlerb.org/minitest/.

\bibitem{serverspec}
``serverspec'', https://github.com/serverspec/serverspec.

\bibitem{nintendo}
``採用情報：キャリア採用 募集要項 - 京都勤務の募集職種 開発部門'',
http://www.nintendo.co.jp/jobs/career/kyoto\_sec1.html\#p03.

\bibitem{wantedly}
serverspecの求人 - Wantedly,
https://www.wantedly.com/projects/search?utf8=%E2%9C%93&q=serverspec.

\bibitem{chef}
``Chef - Code Can | Chef'', http://www.getchef.com/.

\bibitem{ec2}
``Amazon Elastic Compute Cloud'',
http://aws.amazon.com/jp/ec2/.

\bibitem{ruby}
``オブジェクト指向スクリプト言語 Ruby'',
https://www.ruby-lang.org/ja/.

\bibitem{specinfra}
``specinfra'', https://github.com/serverspec/specinfra.

\bibitem{busser-serverspec}
``cl-lab-k/busser-serverspec'',
https://github.com/cl-lab-k/busser-serverspec.

\bibitem{rspec-system-serverspec}
``puppetlabs/rspec-system-serverspec'',
https://github.com/puppetlabs/rspec-system-serverspec.

\bibitem{vagrant}
``Vagrant'',
http://www.vagrantup.com/.

\bibitem{vagrant-serverspec}
``jboorhis/vagrant-servers@ec'',
https://github.com/jvoorhis/vagrant-serverspec.

\bibitem{bats}
``sstephenson/bats'',
https://github.com/sstephenson/bats.

\bibitem{ubuntu}
``The world's most popular free OS | Ubuntu'',
http://www.ubuntu.com/.

\bibitem{solaris}
``Oracle Solaris'',
http://www.oracle.com/jp/products/servers-storage/solaris/overview/index.html.

\end{thebibliography}
